---
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
library(tidyverse)
library(palmerpenguins)
```
### 1. Scatter Plot: Flipper Length vs Body Mass

This scatter plot examines the relationship between a penguin's flipper length and its body mass, categorized by species. It helps us understand whether larger penguins have longer flippers across different breeds.
```
```{r scatter-plot, echo=TRUE}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(
    title = "Flipper Length vs Body Mass by Penguin Species",
    x = "Flipper Length (mm)",
    y = "Body Mass (g)",
    color = "Species"
  ) +
  theme_minimal()
```
### 2. Histogram: Distribution of Body Mass

This histogram shows the frequency distribution of penguin body masses, helping us understand the common weight ranges across the dataset.

```{r histogram, echo=TRUE}
ggplot(penguins, aes(x = body_mass_g, fill = species)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity") +
  labs(
    title = "Distribution of Penguin Body Mass",
    x = "Body Mass (g)",
    y = "Count",
    fill = "Species"
  ) +
  theme_minimal()
```
### 3. Bar Chart: Penguin Count by Island

This bar chart displays the distribution and count of penguin species across different islands in the Palmer Archipelago.

```{r bar-chart, echo=TRUE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position = "dodge") +
  labs(
    title = "Penguin Count by Island and Species",
    x = "Island",
    y = "Count",
    fill = "Species"
  ) +
  theme_minimal()
```
### 4. Box Plot: Bill Length Distribution by Species

This box plot compares the distribution of bill lengths across the three penguin species, highlighting median values and potential outliers.

```{r box-plot, echo=TRUE}
ggplot(penguins, aes(x = species, y = bill_length_mm, fill = species)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Bill Length Distribution by Species",
    x = "Species",
    y = "Bill Length (mm)",
    fill = "Species"
  ) +
  theme_minimal()
```
  